Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-27 docs/_tex/index.tex
add results

The Generalized Linear Model (GLM) analysis revealed a significant
effect of pixel resolution on the agreement, with a negative
relationship (\[\beta = -1.0334 \times 10^{-8}, p < 0.001\]). This
indicates that as pixel resolution increases, the proportion of the
response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement.
Magnoliopsida showed a significant positive effect
(\[\beta = 0.1202, p < 0.001\]), suggesting that this class was
associated with a higher agreement.

>>>>

The Generalized Linear Model (GLM) analysis revealed a significant
effect of pixel resolution on the agreement, with a negative
relationship (\(\beta = -1.0334 \times 10^{-8}, p < 0.001\)). This
indicates that as pixel resolution increases, the proportion of the
response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement.
Magnoliopsida showed a significant positive effect
(\(\beta = 0.1202, p < 0.001\)), suggesting that this class was
associated with a higher agreement.

### 2024-09-27 index.qmd
add results

The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($$\beta = -1.0334 \times 10^{-8}, p < 0.001$$). This indicates that as pixel resolution increases, the proportion of the response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement. Magnoliopsida showed a significant positive effect ($$\beta = 0.1202, p < 0.001$$), suggesting that this class was associated with a higher agreement.

>>>>

The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($\beta = -1.0334 \times 10^{-8}, p < 0.001$). This indicates that as pixel resolution increases, the proportion of the response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement. Magnoliopsida showed a significant positive effect ($\beta = 0.1202, p < 0.001$), suggesting that this class was associated with a higher agreement.
